
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\parskip}{0pt}
\setlength{\parindent}{0pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\flushbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}
  {\vspace{-6pt}\scshape\raggedright\large\bfseries}
  {}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item \small #1
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% ===== LIST CONTROLS (CLEAN & BALANCED) =====
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in,label={},itemsep=3pt,topsep=3pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*,itemsep=2pt,topsep=2pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}}


%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
{\Huge \scshape Ayush Barai} \\ \vspace{0pt}

\raisebox{-0.1\height}\faPhone\ +91 93594 86070 ~ \href{mailto:baraiayush541@Gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{ayushbcse2024@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/ayush-barai-166994175/}{\raisebox{-0.2\height}\faLinkedin\ \underline{Linkedin}}  ~
    \href{https://github.com/AyushBarai}{\raisebox{-0.2\height}\faGithub\ \underline{Github}{\bf }} ~
    \href{https://leetcode.com/u/Ayush_Barai/}{\raisebox{-0.2\height}\faCode\ \underline{Leetcode}{\bf }} ~
    \vspace{1pt}\\
    {GATE 2025 Qualified}
\vspace{-10pt}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Technical Skills}
\textbf{Languages:} Java, Python, C++, JavaScript, TypeScript, SQL \\
\textbf{Backend:} Spring Boot, Flask, Node.js, REST APIs, Microservices, API Design \\
\textbf{Frontend:} React.js, Next.js, Tailwind CSS \\
\textbf{Cloud \& DevOps:} AWS (EC2, S3, WorkMail), Git, Linux, CI/CD (Jenkins, GitHub Actions) \\
\textbf{Databases:} PostgreSQL, MySQL, MongoDB \\
\textbf{Core CS:} Data Structures, Algorithms, OOP, OS, Networking (TCP/IP, HTTP, DNS), SDLC, Agile \\
\textbf{Concepts:} Scalable Systems, High Availability, Distributed Systems Basics, SaaS Platforms, AI \& Emerging Tech: Generative AI Awareness, AI Fundamentals \\

%-----------EXPERIENCE-----------
\vspace{-8pt}
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{CGI}{Jul 2024 -- Present}
{Associate Software Engineer}{Bangalore}
\resumeItemListStart
\resumeItem{Optimized scalable backend services in Java and Spring Boot, reducing incident resolution time by 30\%.}
\resumeItem{Ensured 99.5\% uptime for critical financial systems through proactive monitoring, debugging, and reliability improvements.}
\resumeItem{Modernized legacy applications into microservices architecture, improving deployment efficiency and service modularity.}
\resumeItem{Developed and maintained RESTful APIs enabling secure integration with downstream financial platforms.}
\resumeItem{Collaborated in Agile/Scrum teams to deliver high-quality features in fast-paced production environments.}
\resumeItemListEnd
\vspace{-8pt}
\resumeSubheading
{Prime Groups}{Jan 2024 -- Jun 2024}
{Software Engineer Intern}{Remote}
\resumeItemListStart
\resumeItem{Built and deployed a scalable full-stack web application using Next.js, Node.js, and AWS, increasing user engagement 2× and traffic by 75\%.}
\resumeItem{Developed responsive React-based UI components in collaboration with designers to improve user experience.}
\resumeItem{Designed RESTful backend APIs integrated with AWS cloud services for secure communications.}
\resumeItem{Implemented MySQL and MongoDB for dynamic content management in a SaaS-style environment.}
\resumeItemListEnd
\vspace{-8pt}
\resumeSubheading
{Tech Mahindra}{Dec 2022 -- Feb 2023}
{Student Trainee}{Bangalore}
\resumeItemListStart
\resumeItem{Developed an Android-based fraud detection feature using Kotlin/Java, reducing scams by 70\%.}
\resumeItem{Integrated the module with existing systems, ensuring 100\% compatibility and zero false positives.}
\resumeItem{Built backend logic in Java/Kotlin leveraging APIs for financial system integration.}
\resumeItemListEnd

\resumeSubHeadingListEnd

  %-----------EDUCATION-----------
\vspace{-8pt}
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{B.E. in Computer Science Engineering}{2020 -- 2024}
{The Oxford College of Engineering}{CGPA: 8.5/10}

\resumeSubheading
{xCS50 : Computer Science — Harvard University (edX)}{Remote}
{}{}

\resumeSubHeadingListEnd
\vspace{-10pt}
\textbf{GATE 2025: Qualified (Computer Science)}



%-----------PROJECTS-----------
\vspace{-8pt}
\section{Projects}  
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{AI Based Tic-Tac-Toe using min-max algorithm}}{}
          \resumeItemListStart
            \resumeItem{Implemented the Minimax algorithm with alpha-beta pruning, achieving an 85\% win rate.}
            \resumeItem{Optimized performance by reducing CPU usage by 20\% through efficient state evaluation.}
          \resumeItemListEnd
          \vspace{-6pt}
    \resumeProjectHeading
          {\textbf{Hospital Management System - Backend-powered hospital management system (Python, Flask, MySQL)}}{}
          \resumeItemListStart        
            \resumeItem{Streamlined patient data workflows, cutting wait times by 60\% and paperwork errors by 40\%.}
            \resumeItem{Designed REST APIs for patient data handling and improved data reliability by 40\%.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd
%-----------CERTIFICATION-----------
\vspace{-8pt}
\section{Achievements \& Certifications}
\resumeItemListStart
\resumeItem{Solved 700+ Data Structures \& Algorithms problems across LeetCode and other platforms.}\\[-2pt]
\resumeItem{Ideathon Winner: Designed an ambulance detection system using computer vision, reducing emergency response by 70\%.}\\[-2pt]
\resumeItem{Google IT Automation with Python Specialization — Coursera.}\\[-2pt]
\resumeItem{Open Source Software Development Methods — Linux Foundation.}\\[-2pt]
\resumeItem{Increased brand outreach by 80\% at Prime Groups via targeted initiatives.}\\[-2pt]
\resumeItemListEnd
\end{document}
